### 2021-11-13 NSF2021/Description/specificaim1.tex
repaired figures: pdf -> jpg

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
 \caption{\label{fig:flow_map}
   In the HAP formulation, hydronamic interactions
   come from the Stokes equations and
   hydrophobic interactions come from the structure order parameter $u$.}
\end{wrapfigure}

@@

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional take the form 
\begin{align*}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align*}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

@@

\begin{wrapfigure}[11]{r}{0.65\textwidth}
  \vspace{-10pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow is its director.}
\end{wrapfigure}

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
      (a)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.pdf}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.pdf}
     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.pdf}    \\
     (b)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.pdf}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.pdf}    \\
    (c)
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.pdf}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
  \end{tabular}
    \end{center}
  \caption{\label{fig:self-assembly}
    Using the same initial configuration,
    particles self-assemble into distinct morphologies based
    on the boundart condition $g.$ 
    boundary condition leads to a checkerboard pattern.
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.
  }
\end{figure}

>>>>

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation, hydronamic interactions
   come from the Stokes equations and
   hydrophobic interactions come from the structure order parameter $u$.
   The colormap is for the intensity of $u$.}
\end{wrapfigure}

@@

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{align*}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align*}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

@@

\begin{wrapfigure}[11]{r}{0.65\textwidth}
  \vspace{-10pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow is its director.}
\end{wrapfigure}

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
      (a)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
  \end{tabular}
    \end{center}
  \caption{\label{fig:self-assembly}
    Using the same initial configuration,
    particles self-assemble into distinct morphologies based
    on the boundart condition $g.$ 
    boundary condition leads to a checkerboard pattern.
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.
  }
\end{figure}
